Experimentally informed site-specific substitution models deepen phylogenetic estimates of the divergence of viral lineages

### 2018-02-27 manuscript/manuscript.tex
fixed reference line in phylobayes figure
add in line reference to supp figures

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figures/empirical_trees.pdf}}
\caption{\label{fig:empirical_trees}
\textbf{Effect of site-specific stationary state and $\Gamma\omega$ rate variation on HA branch length estimation.} 
The branch lengths of the HA tree are optimized using the indicated ExpCM and GY94 models. 
The amino-acid preferences defining the model (ExpCM) or implied by the model (GY94) are shown as logoplots for \jdbcomment{? example sites in HA; the full set of experimentally measured amino-acid preferences defining each ExpCM are shown in ?}. 
The ExpCM's use amino-acid preferences measured in deep mutational scanning of an H1 HA~\cite{doud2016accurate}, an H3 HA~\citep{lee2018deep}, or the average of the measurements for these two HAs.
The circle denotes the H1 clade and the triangle denotes the H3 clade. 
}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.5\textwidth]{figures/phylobayes.pdf}}
\caption{\label{fig:phylobayes}
\textbf{Comparison of ExpCM and \texttt{phylobayes}}
We estimated the branch lengths of the HA tree in \ref{fig:empirical_trees} using the mutation-selection model implemented in \texttt{phylobayes}. 
In comparison to ExpCM's, the \texttt{phylobayes} model infers the site-specific amino-acid preferences from the phylogenetic data rather than defining them \textit{a priori} from deep mutational scanning experiments. 
\jdbcomment{The diagonal dotted line is too faint}
}
\end{figure}

@@

\begin{suppfig}[H]
\centerline{\includegraphics[width=\textwidth]{figures/prefs_average}}
\caption{\label{fig:prefs_average}
\textbf{The average of the H1 preferences measured by \cite{doud2016accurate} and the H3 preferences measured by \textit{Lee} rescaled with the ExpCM stringency parameter optimized in \ref{fig:tree_average}A  ($\beta = 1.77$)}}
\end{suppfig}

>>>>

\begin{figure}
\centerline{\includegraphics[width=\textwidth]{figures/empirical_trees.pdf}}
\caption{\label{fig:empirical_trees}
\textbf{Effect of site-specific stationary state and $\Gamma\omega$ rate variation on HA branch length estimation.} 
The branch lengths of the HA tree are optimized using the indicated ExpCM and GY94 models. 
The amino-acid preferences defining the model (ExpCM) or implied by the model (GY94) are shown as logoplots for 15 example sites in HA; the full set of experimentally measured amino-acid preferences defining each ExpCM are shown in \ref{suppfig:prefs_doud}, \ref{suppfig:prefs_lee}, and \ref{suppfig:prefs_average}. 
The ExpCM's use amino-acid preferences measured in deep mutational scanning of an H1 HA~\cite{doud2016accurate}, an H3 HA~\citep{lee2018deep}, or the average of the measurements for these two HAs.
The circle denotes the H1 clade and the triangle denotes the H3 clade. 
}
\end{figure}

@@

\begin{figure}
\centerline{\includegraphics[width=0.5\textwidth]{figures/phylobayes.pdf}}
\caption{\label{fig:phylobayes}
\textbf{Comparison of ExpCM and \texttt{phylobayes}}
We estimated the branch lengths of the HA tree in \ref{fig:empirical_trees} using the mutation-selection model implemented in \texttt{phylobayes}. 
In comparison to ExpCM's, the \texttt{phylobayes} model infers the site-specific amino-acid preferences from the phylogenetic data rather than defining them \textit{a priori} from deep mutational scanning experiments. 
}
\end{figure}

@@

\begin{suppfig}[H]
\centerline{\includegraphics[width=\textwidth]{figures/prefs_average}}
\caption{\label{suppfig:prefs_average}
\textbf{The average of the H1 preferences measured by \cite{doud2016accurate} and the H3 preferences measured by \textit{Lee} rescaled with the ExpCM stringency parameter optimized in \ref{fig:tree_average}A  ($\beta = 1.77$)}}
\end{suppfig}
